\langname: A Language for Multi-View Architecture Description and Control

### 2017-08-01 paper.tex
Selva add

\documentclass[preprint]{sigplanconf}
% The following \documentclass options may be useful:
% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}

\colorlet{light-gray}{gray!20}
\newcommand{\cL}{{\cal L}}

@@

\title{Trinity: A Language for Multi-View Architecture Description and Control}%\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

\authorinfo{Name1}%\thanks{with optional author note}}
           {Affiliation1}
           {Email1}
\authorinfo{Name2 \and Name3}%\thanks{with optional author note}}
           {Affiliation2/3}
           {Email2/3}

@@

%%% *** COMMENTED OUT ***
%\ccsdesc[500]{Software and its engineering~General programming languages}
%\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

@@

%%% COMMENTED OUT
%\keywords
%keyword1, keyword2

\section{Introduction}

\section{Design}

	Trinity is designed to unify software architecture design and implementation for not just a single architecture view, but in all three (module, component-and-connector, and deployment).

	To demonstrate how Trinity makes software architecture “live” in Wyvern systems, we have implemented a simple 3-tier web application whose abridged code is shown in Figure 1. In overview, a database is accessed by a server that handles requests from a client. The example architecture contains two components, the client and server. As in more theoretical software architecture, components are runtime entities that may have ports  that act as access points to interact with other components. Our example server and client each have complementary ports, sendInfo and getInfo respectively, that enable interact; here, the server can send information to the client using a JSON connector responsible for serialization and deserialization. Note that Trinity connectors enable the joining two compatible component ports, analogous to ports in software architecture. The architecture’s attachments section actually/physically connects the client and the server using their matching ports and the JSON connector.

	The client and server have their own component-specific architectures given before the general architecture code. Both components have corresponding ports that depend on a client-server interface, denoted by the “requires/provides CSIface” types of each port. This interface is required of a server by the client, as stated by the “requires CSIFace” type, and the server fulfills it, as shown by the “provides CSIface” server port type. The database is an external component of the server, which differs from a component in that the programmer does not provide its source code. “port dbIface: requires DBModule” The database and server are connected by a JDBC connector. This is used within a sub-architecture of the server that connects a specified request handler and the database. Finally, the bindings section of the server’s sub-architecture specifies that the client-facing port, sendInfo, of the server component is indeed the same sendInfo port of the request handler.

\begin{figure}

	\begin{lstlisting}[frame=single, backgroundcolor=\color{light-gray}, basicstyle=\footnotesize\ttfamily, numbers=left, numberstyle=\tiny\color{black},caption= {Simple 3-tier web application architecture}]
	component Client
	port getInfo: requires CSIface

	component Server
	port sendInfo: provides CSIface

	external component DB
	port dbIface: target DBModule

	connector JDBCCtr
	val connectionString: String

	architecture 
	components
	RequestHandler ch
	DB db

	connectors 
	JDBCCtr jdbcCtr

	attachments
	connect rh.dbIface and db.dbIface 
	with jdbcCtr

	bindings 
	sendInfo is rh.sendInfo

	architecture 	
	components
	Client client
	Server server

	connectors
	JSONCtr jsonCtr

	attachments 
	Connect client.getInfo 
	and server.sendInfo with jsonCtr

	entryPoints
	Client: start
	\end{lstlisting}

\end{figure}

\appendix
\section{Appendix Title}

@@

\bibliographystyle{abbrvnat}

@@

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

>>>>

\documentclass[preprint]{sigplanconf}

% The following \documentclass options may be useful:

% preprint       Remove this option only once the paper is in final form.
%  9pt           Set paper in  9-point type (instead of default 10-point)
% 11pt           Set paper in 11-point type (instead of default 10-point).
% numbers        Produce numeric citations with natbib (instead of default author/year).
% authorversion  Prepare an author version, with appropriate copyright-space text.

\usepackage{amsmath}

\newcommand{\cL}{{\cal L}}
\newcommand{\langname}{Trinity}

@@

%\title{Title Text\titlenote{with optional title note}}
\title{\langname: A Language for Multi-View Architecture Description and Control}
%\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

%\authorinfo{Name1\thanks{with optional author note}}
%           {Affiliation1}
%           {Email1}
%\authorinfo{Name2 \and Name3\thanks{with optional author note}}
%           {Affiliation2/3}
%           {Email2/3}
\authorinfo{Jonathan Aldrich}
           {Carnegie Mellon University}
           {jonathan.aldrich@cs.cmu.edu}
\authorinfo{Madaline Kirwin}
           {Grinnell College}
           {kirwinma@grinnell.edu}
\authorinfo{Selva Samuel}
           {Carnegie Mellon University}
           {ssamuel@cs.cmu.edu}

@@

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Theory of computation~Program analysis}
% end generated code

@@

\keywords
keyword1, keyword2

%\section{Introduction}

%The text of the paper begins here.

\section{Multiple Views of Software Architecture}

\begin{itemize}
\renewcommand\labelitemi{--}
\item Give the SEI definition of software architecture
\item State the usefulness of software architecture in analysis and design activities
\item Introduce ADLs.
\item Introduce views. State their usefulness in dealing with complexity by separating concerns
\item State the lack of support for multiple views in ADLs.
\item State that industry practitioners desire support for multiple views. Cite study by Malavolta et. al.
\end{itemize}
The software architecture of a system is the set of structures needed to reason about the system, which comprise software elements, relations among them, and properties of both [].

%Most software architectures are implicit.

%UML
\cite{Malavolta2013}

\section{Architectural Control}
\begin{itemize}
\renewcommand\labelitemi{--}
\item What is architectural control? --$>$ Architectural constraints must be enforced in the implementation
\item Introduce communication integrity
\item Describe ArchJava's support for enforcing communication integrity in a single JVM and its failure to do so across multiple JVMs
\end{itemize}
\section{\langname}

%\appendix
%\section{Appendix Title}

@@

\bibliographystyle{abbrvnat}
\bibliography{references.bib}

@@

%\begin{thebibliography}{}
%\softraggedright

%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...

%\end{thebibliography}
